---
title: "Find the latest unique client for follow up"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Find-latest-unique-clients}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Finding the latest unique client records is one of the first steps in determining the clients required for a followed up. The current A360 database combines both information captured during the first and the subsequent visit. Clients are identified by `Girl id` and their records are stored as single observation. It is therefore possible to find more than one client with the same `Girl ID`.

To find the latest unique client record, we first identify all the A360 clients using the `Girl ID`. This will help to identify the unique clients from the possible duplicates. We then match the possible duplicates by `Name of Girl` and update the latest file in case there are any missing fields captured in the previous records.

Since the `girl id` and `name` could be duplicated as well, we use the `Phone Number` to confirm the uniqueness of the records and return the latest by `Date of Service Provision`. 

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(a360connect)

a360ngdata <- data.table::fread("/Users/isaiahnyabuto/Documents/Packages/a360connect/tests/testthat/test_data/current_program_a360_full_data.csv")

latest_events <- find_latest_evnt(a360ngdata[1:1000,])

latest_events
```


